Mining Planet Search Data for Binary Stars: The $\psi^1$ Draconis system [UPDATE PLOTS!]

### 2015-08-27 paper/ms.tex
Table 1 includes both the raw and shifted radial velocity measurements.

We used the \emph{Austral} code \citep{Endl2000} to measure the differential radial velocity of $\psi^1$ Dra A at each observation. We provide the velocity measurements after shifting into the system velocity rest frame in Table \ref{tab:rv_data}. The velocity shift necessary to convert from the differential radial velocities to this frame is found in Section \ref{sec:orbit}. Table 1 also gives the measurements of the companion radial velocity (described in the next section).

\begin{deluxetable}{lrrrr}
\tabletypesize{\footnotesize}
\tablewidth{0pt}
%\tablenum{1}
\tablecaption{Observations of $\psi^1$ Dra A \label{tab:rv_data}}
\tablehead{
\colhead{Julian Date} & \colhead{ $v_1$ }  & \colhead{$\sigma_{v_1}$ } & \colhead{ $v_2$ }  & \colhead{$\sigma_{v_2}$ }  \\
 & \colhead{(m/s)}  & \colhead{(m/s)} & \colhead{(m/s)}  & \colhead{(m/s)} }

@@

 2451809.66 &  -2.174 &   0.013 &  \nodata &  \nodata \\
 2451809.67 &  -2.172 &   0.014 &  \nodata &  \nodata \\
 2452142.68 &  -2.259 &   0.012 &  \nodata &  \nodata \\
 2453319.64 &  -1.668 &   0.011 &  \nodata &  \nodata \\
 2453585.85 &  -1.542 &   0.010 &  \nodata &  \nodata \\
 2453585.88 &  -1.551 &   0.011 &  \nodata &  \nodata \\
 2453634.64 &  -1.446 &   0.011 &  \nodata &  \nodata \\
 2453635.62 &  -1.547 &   0.009 &  \nodata &  \nodata \\
 2453655.64 &  -1.390 &   0.009 &  \nodata &  \nodata \\
 2453655.64 &  -1.321 &   0.027 &  \nodata &  \nodata \\
 2453689.54 &  -1.436 &   0.008 &  \nodata &  \nodata \\
 2453907.85 &  -1.141 &   0.011 &  \nodata &  \nodata \\
 2453928.80 &  -1.243 &   0.012 &  \nodata &  \nodata \\
 2454019.60 &  -1.171 &   0.012 &  \nodata &  \nodata \\
 2454279.75 &  -1.033 &   0.011 &  \nodata &  \nodata \\
 2454279.76 &  -1.044 &   0.010 &  \nodata &  \nodata \\
 2454309.79 &  -1.080 &   0.013 &  \nodata &  \nodata \\
 2454345.63 &  -0.830 &   0.010 &  \nodata &  \nodata \\
 2454401.56 &  -0.945 &   0.009 &  \nodata &  \nodata \\
 2454662.93 &  -0.752 &   0.015 &     0.36 &     0.37 \\
 2454665.77 &  -0.615 &   0.014 &     0.75 &     0.35 \\
 2454665.77 &  -0.609 &   0.015 &     0.64 &     0.36 \\
 2454730.71 &  -0.644 &   0.014 &     0.68 &     0.36 \\
 2455100.57 &  -0.226 &   0.016 &     0.04 &     0.44 \\
 2455100.58 &  -0.210 &   0.014 &     0.16 &     0.44 \\
 2455398.75 &   0.108 &   0.015 &    -0.89 &     0.51 \\
 2455790.72 &   0.876 &   0.021 &    -2.34 &     0.67 \\
 2455869.58 &   1.111 &   0.017 &    -1.66 &     0.60 \\
 2455910.57 &   1.221 &   0.018 &    -1.82 &     0.63 \\
 2455992.02 &   1.437 &   0.012 &    -2.22 &     0.65 \\
 2456016.93 &   1.558 &   0.014 &    -2.37 &     0.62 \\
 2456106.78 &   1.683 &   0.015 &    -3.24 &     0.67 \\
 2456138.84 &   1.844 &   0.020 &    -3.51 &     0.73 \\
 2456145.65 &   1.846 &   0.025 &    -4.14 &     0.80 \\
 2456145.66 &   1.828 &   0.018 &    -4.19 &     0.79 \\
 2456145.66 &   1.864 &   0.018 &    -3.91 &     0.79 \\
 2456173.73 &   1.854 &   0.018 &    -3.48 &     0.75 \\
 2456401.97 &   2.864 &   0.014 &    -5.87 &     0.69 \\

@@

\begin{deluxetable}{lrrrr}
\tabletypesize{\footnotesize}
\tablewidth{0pt}
\tablenum{1}
\tablecaption{Observations of $\psi^1$ Dra A (continued)}
\tablehead{
\colhead{Julian Date} & \colhead{ $v_1$ }  & \colhead{$\sigma_{v_1}$ } & \colhead{ $v_2$ }  & \colhead{$\sigma_{v_2}$ }  \\
 & \colhead{(m/s)}  & \colhead{(m/s)} & \colhead{(m/s)}  & \colhead{(m/s)} }

@@

 2456401.97 &   2.841 &   0.012 &    -6.15 &     0.68 \\
 2456433.74 &   3.138 &   0.013 &    -6.14 &     0.62 \\
 2456433.74 &   3.108 &   0.012 &    -6.21 &     0.65 \\
 2456435.87 &   3.108 &   0.015 &    -6.33 &     0.64 \\
 2456435.87 &   3.104 &   0.015 &    -6.68 &     0.64 \\
 2456461.87 &   3.257 &   0.012 &    -6.42 &     0.63 \\
 2456461.88 &   3.250 &   0.015 &    -6.11 &     0.65 \\
 2456461.88 &   3.225 &   0.016 &    -6.06 &     0.61 \\
 2456465.80 &   3.196 &   0.014 &    -6.18 &     0.53 \\
 2456497.86 &   3.473 &   0.019 &    -7.13 &     0.73 \\
 2456519.62 &   3.664 &   0.015 &    -7.93 &     0.59 \\
 2456525.66 &   3.624 &   0.017 &    -7.38 &     0.64 \\
 2456560.58 &   3.711 &   0.013 &    -7.22 &     0.90 \\
 2456564.59 &   3.680 &   0.015 &    -7.05 &     0.86 \\
 2456613.55 &   3.988 &   0.016 &    -6.51 &     0.91 \\
 2456614.58 &   4.038 &   0.012 &    -7.06 &     0.85 \\
 2456755.98 &   5.208 &   0.014 &   -10.84 &     0.74 \\
 2456759.97 &   5.265 &   0.015 &   -11.28 &     0.76 \\
 2456784.84 &   5.502 &   0.017 &   -11.69 &     0.81 \\
 2456816.67 &   5.794 &   0.014 &   -12.17 &     0.74 \\
 2456816.67 &   5.806 &   0.015 &   -12.49 &     0.72 \\
 2456860.73 &   6.301 &   0.016 &   -13.97 &     0.88 \\
 2456860.73 &   6.321 &   0.015 &   -14.11 &     0.83 \\
 2456885.62 &   6.507 &   0.015 &   -15.29 &     0.84 \\
 2456938.63 &   7.089 &   0.016 &   -16.77 &     1.03 \\
 2456938.64 &   7.072 &   0.015 &   -16.45 &     0.96 \\
 2457092.02 &   8.013 &   0.015 &   -18.09 &     1.00 \\
 2457109.85 &   7.976 &   0.015 &   -19.40 &     1.10 \\
 2457118.96 &   7.886 &   0.016 &   -17.82 &     0.90 \\
 2457150.92 &   7.584 &   0.017 &  \nodata &  \nodata \\
 2457174.96 &   7.167 &   0.017 &   -16.13 &     0.81 \\
 2457214.83 &   6.139 &   0.017 &   -13.16 &     0.82 \\
 2457214.84 &   6.152 &   0.016 &   -13.85 &     0.90 \\
 2457216.73 &   6.119 &   0.016 &   -13.66 &     0.86 \\
 2457216.73 &   6.128 &   0.015 &   -13.69 &     0.80 \\
 2457245.60 &   5.201 &   0.016 &   -11.52 &     0.77 \\
 2457245.61 &   5.199 &   0.016 &   -11.16 &     0.72 \\
 2457248.61 &   5.237 &   0.017 &   -11.05 &     0.70 \\

\tablecomments{The velocities given here are shifted into the system velocity rest frame using the results of the analysis presented in Section \ref{sec:orbit}. The raw radial velocity data is available at \url{https://github.com/kgullikson88/Planet-Finder}}
\end{deluxetable}

@@

We give the companion velocities in Table \ref{tab:rv_data}, after converting from $v_{m, 2}$ to $v_2$ using Equation \ref{eqn:vel} and the results of the analysis described below. The uncertainties given in Table \ref{tab:rv_data} are determined from the CCF peak width and the scaling factor ($f$) derived below. Both the primary and secondary velocities given in Table \ref{tab:rv_data} are for the reader's convenience; we use the raw measurements in the orbital fit.

>>>>

We used the \emph{Austral} code \citep{Endl2000} to measure the differential radial velocity of $\psi^1$ Dra A at each observation. We provide the raw velocity measurements in Table \ref{tab:rv_data}, as well as the velocities shifted into the system velocity rest frame. The velocity shift necessary to convert from the differential radial velocities to this frame is found in Section \ref{sec:orbit}. Table \ref{tab:rv_data} also gives the measurements of the companion radial velocity (described in the next section).

\begin{deluxetable}{lrrrrrr}
\tabletypesize{\footnotesize}
\tablewidth{0pt}
%\tablenum{1}
\tablecaption{Observations of $\psi^1$ Dra A \label{tab:rv_data}}
\tablehead{
\colhead{Julian Date} & \multicolumn{3}{c}{Primary RV (m/s)} & \multicolumn{3}{c}{Secondary RV (m/s)} \\
& \colhead{raw} & \colhead{shifted} & \colhead{$\sigma$}  & \colhead{raw} & \colhead{shifted}  & \colhead{$\sigma$} }

@@

 2451809.66 &   1.927 &  -2.174 &   0.013 &  \nodata &  \nodata &  \nodata \\
 2451809.67 &   1.929 &  -2.172 &   0.014 &  \nodata &  \nodata &  \nodata \\
 2452142.68 &   1.841 &  -2.259 &   0.012 &  \nodata &  \nodata &  \nodata \\
 2453319.64 &   2.433 &  -1.668 &   0.011 &  \nodata &  \nodata &  \nodata \\
 2453585.85 &   2.559 &  -1.542 &   0.010 &  \nodata &  \nodata &  \nodata \\
 2453585.88 &   2.550 &  -1.551 &   0.011 &  \nodata &  \nodata &  \nodata \\
 2453634.64 &   2.654 &  -1.446 &   0.011 &  \nodata &  \nodata &  \nodata \\
 2453635.62 &   2.554 &  -1.547 &   0.009 &  \nodata &  \nodata &  \nodata \\
 2453655.64 &   2.711 &  -1.390 &   0.009 &  \nodata &  \nodata &  \nodata \\
 2453655.64 &   2.780 &  -1.321 &   0.027 &  \nodata &  \nodata &  \nodata \\
 2453689.54 &   2.665 &  -1.436 &   0.008 &  \nodata &  \nodata &  \nodata \\
 2453907.85 &   2.960 &  -1.141 &   0.011 &  \nodata &  \nodata &  \nodata \\
 2453928.80 &   2.858 &  -1.243 &   0.012 &  \nodata &  \nodata &  \nodata \\
 2454019.60 &   2.930 &  -1.171 &   0.012 &  \nodata &  \nodata &  \nodata \\
 2454279.75 &   3.068 &  -1.033 &   0.011 &  \nodata &  \nodata &  \nodata \\
 2454279.76 &   3.056 &  -1.044 &   0.010 &  \nodata &  \nodata &  \nodata \\
 2454309.79 &   3.021 &  -1.080 &   0.013 &  \nodata &  \nodata &  \nodata \\
 2454345.63 &   3.270 &  -0.830 &   0.010 &  \nodata &  \nodata &  \nodata \\
 2454401.56 &   3.155 &  -0.945 &   0.009 &  \nodata &  \nodata &  \nodata \\
 2454662.93 &   3.349 &  -0.752 &   0.015 &    -4.34 &     0.36 &     0.37 \\
 2454665.77 &   3.486 &  -0.615 &   0.014 &    -3.95 &     0.75 &     0.35 \\
 2454665.77 &   3.492 &  -0.609 &   0.015 &    -4.06 &     0.64 &     0.36 \\
 2454730.71 &   3.457 &  -0.644 &   0.014 &    -4.09 &     0.68 &     0.36 \\
 2455100.57 &   3.875 &  -0.226 &   0.016 &    -5.14 &     0.04 &     0.44 \\
 2455100.58 &   3.891 &  -0.210 &   0.014 &    -5.02 &     0.16 &     0.44 \\
 2455398.75 &   4.209 &   0.108 &   0.015 &    -6.49 &    -0.89 &     0.51 \\
 2455790.72 &   4.977 &   0.876 &   0.021 &    -8.65 &    -2.34 &     0.67 \\
 2455869.58 &   5.211 &   1.111 &   0.017 &    -8.14 &    -1.66 &     0.60 \\
 2455910.57 &   5.321 &   1.221 &   0.018 &    -8.40 &    -1.82 &     0.63 \\
 2455992.02 &   5.538 &   1.437 &   0.012 &    -9.01 &    -2.22 &     0.65 \\
 2456016.93 &   5.659 &   1.558 &   0.014 &    -9.23 &    -2.37 &     0.62 \\
 2456106.78 &   5.784 &   1.683 &   0.015 &   -10.36 &    -3.24 &     0.67 \\
 2456138.84 &   5.944 &   1.844 &   0.020 &   -10.73 &    -3.51 &     0.73 \\
 2456145.65 &   5.947 &   1.846 &   0.025 &   -11.38 &    -4.14 &     0.80 \\
 2456145.66 &   5.929 &   1.828 &   0.018 &   -11.43 &    -4.19 &     0.79 \\
 2456145.66 &   5.965 &   1.864 &   0.018 &   -11.15 &    -3.91 &     0.79 \\
 2456173.73 &   5.955 &   1.854 &   0.018 &   -10.82 &    -3.48 &     0.75 \\
 2456401.97 &   6.964 &   2.864 &   0.014 &   -14.11 &    -5.87 &     0.69 \\

@@

\begin{deluxetable}{lrrrrrr}
\tabletypesize{\footnotesize}
\tablewidth{0pt}
\tablenum{1}
\tablecaption{Observations of $\psi^1$ Dra A (continued)}
\tablehead{
\colhead{Julian Date} & \multicolumn{3}{c}{Primary RV (m/s)} & \multicolumn{3}{c}{Secondary RV (m/s)} \\
& \colhead{raw} & \colhead{shifted} & \colhead{$\sigma$}  & \colhead{raw} & \colhead{shifted}  & \colhead{$\sigma$} }

@@

 2456401.97 &   6.941 &   2.841 &   0.012 &   -14.39 &    -6.15 &     0.68 \\
 2456433.74 &   7.238 &   3.138 &   0.013 &   -14.54 &    -6.14 &     0.62 \\
 2456433.74 &   7.209 &   3.108 &   0.012 &   -14.61 &    -6.21 &     0.65 \\
 2456435.87 &   7.208 &   3.108 &   0.015 &   -14.73 &    -6.33 &     0.64 \\
 2456435.87 &   7.205 &   3.104 &   0.015 &   -15.08 &    -6.68 &     0.64 \\
 2456461.87 &   7.358 &   3.257 &   0.012 &   -14.96 &    -6.42 &     0.63 \\
 2456461.88 &   7.351 &   3.250 &   0.015 &   -14.65 &    -6.11 &     0.65 \\
 2456461.88 &   7.326 &   3.225 &   0.016 &   -14.60 &    -6.06 &     0.61 \\
 2456465.80 &   7.297 &   3.196 &   0.014 &   -14.74 &    -6.18 &     0.53 \\
 2456497.86 &   7.574 &   3.473 &   0.019 &   -15.86 &    -7.13 &     0.73 \\
 2456519.62 &   7.765 &   3.664 &   0.015 &   -16.78 &    -7.93 &     0.59 \\
 2456525.66 &   7.725 &   3.624 &   0.017 &   -16.27 &    -7.38 &     0.64 \\
 2456560.58 &   7.812 &   3.711 &   0.013 &   -16.32 &    -7.22 &     0.90 \\
 2456564.59 &   7.781 &   3.680 &   0.015 &   -16.18 &    -7.05 &     0.86 \\
 2456613.55 &   8.089 &   3.988 &   0.016 &   -15.96 &    -6.51 &     0.91 \\
 2456614.58 &   8.139 &   4.038 &   0.012 &   -16.52 &    -7.06 &     0.85 \\
 2456755.98 &   9.308 &   5.208 &   0.014 &   -21.44 &   -10.84 &     0.74 \\
 2456759.97 &   9.366 &   5.265 &   0.015 &   -21.91 &   -11.28 &     0.76 \\
 2456784.84 &   9.603 &   5.502 &   0.017 &   -22.56 &   -11.69 &     0.81 \\
 2456816.67 &   9.895 &   5.794 &   0.014 &   -23.36 &   -12.17 &     0.74 \\
 2456816.67 &   9.907 &   5.806 &   0.015 &   -23.68 &   -12.49 &     0.72 \\
 2456860.73 &  10.402 &   6.301 &   0.016 &   -25.64 &   -13.97 &     0.88 \\
 2456860.73 &  10.421 &   6.321 &   0.015 &   -25.77 &   -14.11 &     0.83 \\
 2456885.62 &  10.607 &   6.507 &   0.015 &   -27.23 &   -15.29 &     0.84 \\
 2456938.63 &  11.189 &   7.089 &   0.016 &   -29.30 &   -16.77 &     1.03 \\
 2456938.64 &  11.173 &   7.072 &   0.015 &   -28.99 &   -16.45 &     0.96 \\
 2457092.02 &  12.114 &   8.013 &   0.015 &   -31.57 &   -18.09 &     1.00 \\
 2457109.85 &  12.077 &   7.976 &   0.015 &   -32.79 &   -19.40 &     1.10 \\
 2457118.96 &  11.987 &   7.886 &   0.016 &   -31.14 &   -17.82 &     0.90 \\
 2457150.92 &  11.685 &   7.584 &   0.017 &  \nodata &  \nodata &  \nodata \\
 2457174.96 &  11.267 &   7.167 &   0.017 &   -28.58 &   -16.13 &     0.81 \\
 2457214.83 &  10.240 &   6.139 &   0.017 &   -24.68 &   -13.16 &     0.82 \\
 2457214.84 &  10.253 &   6.152 &   0.016 &   -25.36 &   -13.85 &     0.90 \\
 2457216.73 &  10.220 &   6.119 &   0.016 &   -25.13 &   -13.66 &     0.86 \\
 2457216.73 &  10.228 &   6.128 &   0.015 &   -25.15 &   -13.69 &     0.80 \\
 2457245.60 &   9.302 &   5.201 &   0.016 &   -22.21 &   -11.52 &     0.77 \\
 2457245.61 &   9.299 &   5.199 &   0.016 &   -21.85 &   -11.16 &     0.72 \\
 2457248.61 &   9.338 &   5.237 &   0.017 &   -21.66 &   -11.05 &     0.70 \\
\enddata

\tablecomments{The velocities in the `raw' columns are our actual measurements. Those in the `shifted' columns are shifted into the system velocity rest frame using the results of the orbital fit described in Section \ref{sec:orbit}.}
\end{deluxetable}

@@

We give the measured companion velocities in Table \ref{tab:rv_data} (column 5). We additionally provide the velocities in the system velocity rest frame ($v_2$) by using Equation \ref{eqn:vel} and the results of the analysis described below. The uncertainties given in Table \ref{tab:rv_data} are determined from the CCF peak width and the scaling factor ($f$) derived below. The shifted primary and secondary velocities given in Table \ref{tab:rv_data} are for the reader's convenience since they are in the same reference frame; we use the raw measurements in the orbital fit.
